Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-09-08 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:09:08	11:12:04	(Tue 8.Sep)

Two different scenes will be presented. One of the 1500 DWT oil tanker wreck Holmengraa lying at a slanted seabed at 77\;m depth outside of Horten, Norway~\cite{holmengraa}. It measures 68\;m by 9\;m and fills most of the highlighted sector. The other scene is of an iron cross of 1\,m length in both directions, connected to a an anchor with a 13\,cm diameter (\Fig{cross}).

MVDR was run with a fairly aggressive yet stable set of parameters; subarray size $L=16$ and $d=1\%$ diagonal loading. Both MVDR and LCA was run with $K=1$ temporal averaging.

The results will be presented in the following order: In section \ref{lca_window_function} we discuss typical window responses computed by MVDR (\Fig{mvdr_selected_windows}), and hypothesize  that these can be mimicked by Kaiser windows. In section \ref{lca_kaiser_parameters} we investigate what sensible boundaries for the Kaiser parameter $\beta$ and window steering $\phi$ should be (\Fig{oversampling_mosaic_bounds}). In section \ref{lca_database_size} we discuss how many variations of windows between the just determined boundaries should be (\Fig{oversampling_mosaic_bounds_beta}), and determine max window database size.

\subsection{Window function}\label{lca_window_function}

Assuming that a robust MVDR is the reference method we want LCA to perform similarly to, it seems sensible to create window database for LCA with responses that resembles that of MVDR. The typical responses MVDR creates for shadow, speckle and highlight regions of a sectorscan Holmengraa image is shown in \Fig{mvdr_selected_windows}.

Observe from \Fig{mvdr_selected_windows} that MVDR seems prefers symmetric window responses, even if it is free to choose non-symmetric ones. The symmetry is most predominant in shadow and speckle regions, while in highlight the windows are approximately symmetric within the illuminated\todo{valid term?} sector of the seafloor. The symmetry is a side-effect of robustifying MVDR to handle coherent interference and the low sample support of covariance statistics.

If we look at the peak sidelobe levels of the MVDR windows they are for the most part between -13\,dB and -43\,dB. This corresponds to that of the rectangular and Hamming window, or a Kaiser window with $\beta=0$ and $\beta=2$, respectively. Using the Kaiser window in this case makes sense since it is optimal in the sense of having its peak power concentration near the steering angle, and because we can also create any response in between. The Kaiser windows are easy to compute, is fairly insensitive to coefficient inaccuracies, and can create windows with shapes spanning from rectangular to Gaussian.

>>>>

Two different scenes will be presented. One of the 1500 DWT oil tanker wreck Holmengraa lying at a slanted seabed at 77\;m depth outside of Horten, Norway~\cite{holmengraa}. It measures 68\;m by 9\;m and fills most of the highlighted sector. The other scene is of an iron cross of 1\,m length in both directions, connected to a an anchor with a 13\,cm diameter (\Fig{cross}). Both scenes is imaged in sectorscan mode.

In the image reconstruction we have run MVDR with a fairly aggressive yet stable set of parameters; subarray size $L=16$ and $d=1\%$ diagonal loading. Both MVDR and LCA was run with $K=1$ temporal averaging.

The results will be presented in the following order: In section \ref{lca_window_function} we discuss typical window responses computed by MVDR (\Fig{mvdr_selected_windows}), and hypothesize  that these can be mimicked by Kaiser windows. In section \ref{lca_kaiser_parameters} we investigate what sensible boundaries for the Kaiser parameter $\beta$ and window steering $\phi$ should be (\Fig{oversampling_mosaic_bounds}). In section \ref{lca_database_size} we discuss how many window variations is needed for LCA to perform well (\Fig{oversampling_mosaic}).

\subsection{LCA window function}\label{lca_window_function}

Assuming that a robust MVDR is the reference method we want LCA to perform similarly to, it seems sensible to create window database for LCA with responses that resembles the ones MVDR computes. We study this in \Fig{mvdr_selected_windows}, where the typical responses MVDR creates for shadow, speckle and highlight regions in the Holmengraa scene is presented.

Observe from \Fig{mvdr_selected_windows} that MVDR seems prefers symmetric window responses, even if it is free to choose non-symmetric ones. The symmetry is most predominant in shadow and speckle regions, while in highlight the windows are approximately symmetric within the illuminated\todo{valid term?} sector of the seafloor. The symmetry is a side-effect of robustifying MVDR to operate in near snapshot mode in an active system. If we look at the peak sidelobe levels of the MVDR windows they are for the most part between -13\,dB and -43\,dB. This corresponds to that of the rectangular and Hamming window, or a Kaiser window with $\beta=0$ and $\beta=2$, respectively.

We hypothesize that LCA should work even if it only selects from Kaiser windows. If they span a decent range of $\beta$-values, and some steering variations is applied to each, we should have responses that resembles those in \Fig{mvdr_selected_windows}. The Kaiser window is easy to compute, is fairly insensitive to coefficient inaccuracies, and can create windows with shapes spanning from rectangular to Gaussian.

it is optimal in the sense of having its peak power concentration near the steering angle
